Data Management for LSST Special Programs

### 2024-03-26 sec_sci.tex
more updates to region labels

\textbf{All visits should have at least one region label \textit{and} one observing mode 
label, and these labels should be propagated to processed images and catalog data.}

\textbf{Region Labels -- } 
Applied to a visit based on its Right Acension and Declination.
To be applied to data by Rubin Data Management using, e.g., a look-up table.
Region labels would include, e.g., WFD low-dust, Galactic Plane, Galactic 
Bulge, SCP, NES, or Virgo; DDF fieldname; mini-survey region name.
A given visit is likely to have multiple region labels because, for example,
the DDFs are within the WFD low-dust region.
These could be stored in, e.g., a single string as a CSV.

@@

For example, for images, the region labels could be propagated to processed images
(e.g., visit, difference, and deep coadds), so that users may query the ObsTAP 
service for all images with a given region label.
For catalogs, the region labels could be stored for individual sources and
objects as a table column, or for TAP-accessible tables stored in a joinable
table such as the Visit, ccdVisit, or coaddPatches tables.
Another option may be to map regions into spatial divisions (htm or healpix),
and enable users to query image and catalog products via their htm.

>>>>

\textbf{All visits should have at least one region label \textit{and} one observing mode 
label, and these labels should be available to users as query constraints for
all images and tables.}

\textbf{Region Labels -- } 
Applied to a visit based on its Right Acension and Declination.

To be applied to data by Rubin Data Management using, e.g., a look-up table.
Region labels would include, e.g., WFD low-dust, Galactic Plane, Galactic 
Bulge, SCP, NES, or Virgo; DDF fieldname; mini-survey region name.
A given visit is likely to have multiple region labels because, for example,
the DDFs are within the WFD low-dust region.
These could be stored in, e.g., a single string as a CSV.

@@

For example, for images, the region labels could be propagated to processed images
(e.g., visit, difference, and deep coadds), so that users may query the ObsTAP 
service for all images with a given region label.
For catalogs, the region labels could be stored for individual sources and
objects as a table column, or for TAP-accessible tables stored in a joinable
table such as the Visit, ccdVisit, or coaddPatches tables.
Another option may be to map regions into spatial divisions (HTM or HEALPix),
and enable users to query image and catalog products this way.

The spatial resolution of region labels is left to be determined as it depends
somewhat on the implementation.
In this document the region label is considered to be applied to a visit
if the visit overlaps the region, as a very simple implementation.
However, the field of view is so large that a finer resolution by ccd,
or by a smaller-mesh HTM map if the regions are determined for sources and objects,
would be possible (and more useful to users).
